\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-10 tex/paper.tex
Added security findings

%}}}
\title{\textbf{Designing a Virtual Security Management Layer for Cloud Content}}
\author{Lukas Klingsbo}

@@

The research question that this report answers is how and whether it is practically feasible to use
Copy-on-Write for a high-level system like the one that is implemented.

@@

When uploading files to the CDN networks, their TLS/SSL protected API's are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to traverse through the tree in Perius.

@@

\subsubsection{Security}
\fix Write what security implications that can be seen

@@

\par The positive effects of deploying Perius instead of its predecessor was not only on about
scaling, it also features a more secure way of handling private assets 
(Section~\ref{sec:current_system},~\ref{sec:private_content}) and reduces the
administration needed to control the security settings of large groups of assets
(Section~\ref{sec:cdn_connections}) at the same time.

>>>>

%}}}
\title{\textbf{Designing a Security Management Layer for CDN Assets}}
\author{Lukas Klingsbo}

@@

The research question that this report tries to answers is how and whether it is practically 
feasible to use Copy-on-Write for a high-level system like the one that is implemented and how 
it can effect the systems scalability.

@@

When uploading files to the CDN networks, their TLS/SSL protected APIs are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to manually traverse through the tree in Perius.

@@

\subsubsection{Security}
The greatest security improvement of Perius compared to its predecessor Battlebinary is not the
security of the system itself but rather how Perius handles the contents security settings on the
CDN providers. Perius uses several of the security features for private content that the CDN
providers offer (see Section~\ref{sec:private_content}) to make sure that the content only is
accessible from where it should be. In Battlebinary the content was secured by adding a part of the
hash of the file (see Section~\ref{sec:current_system}) to the filename that it was uploaded with, 
which resulted in a URL on the CDN that was not guessable but if the link somehow leaked the 
content that the link referred to would be open to anyone.

@@

\par The positive effects of deploying Perius instead of its predecessor was not only about
scaling, it also features a more secure way of handling private assets 
(Section~\ref{sec:current_system},~\ref{sec:private_content}) and reduces the
administration needed to control the security settings of large groups of assets
(Section~\ref{sec:cdn_connections}) at the same time.
